\documentclass[10pt,a4paper]{article}
\usepackage[margin=3cm]{geometry}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}

\newif\ifdraft
\drafttrue
%\draftfalse                                                                              
\ifdraft
\newcommand{\zhaonote}[1]{{\textcolor{green}    { ***Zhao:      #1 }}}
\newcommand{\note}[1]{ {\textcolor{red}    {\bf #1 }}}
\else
\newcommand{\zhaonote}[1]{}
\newcommand{\note}[1]{}
\fi

 \newenvironment{shortlist}{
        \vspace*{-0.5em}
  \begin{itemize}
  \setlength{\itemsep}{-0.1em}
}{
  \end{itemize}
        \vspace*{-0.5em}
}


\title{Scientific Computing Meets Big Data Technology: An Astronomy Use Case}
\author{Zhao Zhang, Kyle Barbary, Frank Austin Nothaft Evan R. Sparks, \\Oliver Zahn, Michael J. Franklin, David A. Patterson, Saul Perlmutter}

\begin{document}
\maketitle
\noindent We are submitting an extended version of the previously published paper~\cite{lamport94} to IEEE Transactions on Big Data.
\subsection*{Summary of Differences}
In this extended version manuscript, we migrated the integration of Kira and Spark from Scala to Python. 
This was mainly for better adoption of Kira in the astronomy community. 
We also improved the data structure and layout, and minimized the data copy between language runtimes.
We measured the performance of the latest Kira, and examined how Solid State Disks can further improve the performance.
Enabled by Spark Streaming, we implemented and evaluated how the same Kira implementation performed when deployed
as a streaming application. 


Specifically, the latest Kira implementation achieves a $\sim$2x speedup compared to the previous version, and it is 1.8x as fast as
the C implementation on the Edison supercomputer. 
Using Solid State Disks can boost the an additional 2x speedup (4x speedup over the previous version.)
The deployment on a 16-node cluster on Amazon Cloud can achieve a latency of 4 seconds with a throughput of $\sim$600~MB/s.

\subsection*{New and Original Contributions}
\begin{itemize}
\item{} Big data technology is promising in supporting data-intensive scientific applications.
The latest Kira achieves a $\sim$5x speedup over the HPC solution on Amazon cloud, 
and it is 1.8x as fast as the C implementation on the Edison supercomputer. 
Besides, using Solid State Disks can boost the an additional 2x speedup.
\item{} With Kira deployed as a streaming application, we studied the tradeoff space between processing latency and throughput.
A deployment on a 16-node cluster on Amazon Cloud can achieve a latency of 4 seconds with a throughput of $\sim$600~MB/s.
\end{itemize}

\subsection*{Percentage of New Material}
We updated manuscript to include the performance measurements of the latest Kira improvements. 
Besides, we evaluate how solid state disks can further improve the performance and explore the performance boundary when Kira
is deployed as a streaming application.
With the newly updated 5-page performance evaluation and the according updates throughout the manuscript, we believe there is more
than 30\% new materials.

\begin{itemize}
\item{} We partially update the abstract, introduction, design and implementation section, and the conclusion to include the latest results.
Specifically, Item 5 in Paragraph 5 in introduction is newly added.
The third paragraph in Section~2.4 is newly added.
Figure 1 is updated.
Section~4.3 is updated with the streaming interface detail.

\item{} Section~8 is completed updated with the measurements of the latest Kira improvements.
Section~8.4 is newly added to include the performance improvement that can be contributed by solid state disks.
Section~8.5 is newly added to present the latency-throughput tradeoff space study when deploying Kira as a streaming application.
\end{itemize}


\begin{thebibliography}{1}

\bibitem{lamport94}
Zhang, Zhao, Kyle Barbary, Frank Austin Nothaft, Evan Sparks, Oliver Zahn, Michael J. Franklin, David A. Patterson, and Saul Perlmutter. "Scientific computing meets big data technology: An astronomy use case." In Big Data (Big Data), 2015 IEEE International Conference on, pp. 918-927. IEEE, 2015.
\end{thebibliography}

\end{document}
